---
title: "Lab 7 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Setup
1. Login to the lab computer (please don't use your personal computer).  
2. Navigate to github.com and login.   
2. Use GitHub desktop to clone your repository to the desktop.   
5. Copy the class repository to the desktop (https://github.com/jmledford3115/datascibiol).  
6. Copy the files for today's lab from the class repository and paste them into **your** repository.  
7. Open today's lab in RStudio.  

## Review from last time
### *With a partner, discuss the following questions*
1. How did the midterm go? Did you learn anything while doing the exam?
it was okay, a bit more difficult than expected but different ways to answer the question presented
2. Where did you get stuck?
around number 4, and the third to last problem 
3. What do we need to practice?
thinking of what to use quickly, and mutate 

### Warm-up
1. Please install the package `naniar`.
```{r}
library(naniar)
```

